\vskip-0.6in \Large Political Uncertainty

### 2015-03-21 GS-extension.tex
add notes on uncertainty from 3/16

\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty:
						\[
						  v(z) = \alpha -\beta \cdot z + \ve_z
						\]
						we can decide later on the distributional assumptions for $\ve_z$, and whether / when we want to make the $\ve$ vary by legislator ($z$)
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

\newpage
Notes from 3/19 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item We can use the data we have to horse-race this model against other hypotheses about how lobbyists distribute bribes
		\begin{itemize}
			\item Allocate equally among legislators
			\item Groseclose Snyder with full information: only one side pays
			\item Our model with one dimension
				\begin{itemize}
					\item Could we use the econometric model to benchmark to one where uncertainty disappears? Or, as it does theoretically, does the model have to change completely?
				\end{itemize}
			\item Our model with multiple dimensions
		\end{itemize}
	\item We can think of this as looking for the effect of uncertainty on prices---we'd be pricing uncertainty relative to a model with uncertainty
		\begin{itemize}
			\item ``a metric in dollars of uncertainty''
			\item this is a model of vote buying under uncertainty
		\end{itemize}
	\item Given how different the environment with uncertainty is, Kristy should explore both the sequential model that parrots GS96 and a simultaneous model that is more like GH94 (menu auction)
	\item When mapping to the data, we're going to want to know from the model whether/when total contributions represent WTP.
		\begin{itemize}
			\item It clearly doesn't in the case of certainty. One side pays nothing; the other pays either as much as is necessary to shut down its opponent, or nothing at all the necessary amount exceeds WTP
			\item May be able to show it doesn't matter, that the proportion of total expenditures is a sufficient statistic
		\end{itemize}
	\item Finish writing the model, and then see if we can use the estimates we already have to write a first, very rough draft
\end{itemize}

>>>>

\vskip.3in
General thoughts on extension to uncertainty
\begin{itemize}
	\item I think, without uncertainty, you would estimate $m^*$ as a function of the parameters of $v$ and WTP
		\begin{itemize}
			\item It's useful that $m^*$ is unique. Not clear it would extend to case of uncertainty, but I think it's likely so I'm going to assume it for now
		\end{itemize}
	\item I'm pretty sure  this predicts that $B$ should never pay anything when there is no uncertainty, but I don't see where they say it explicitly (I should read more carefully to verify)
		\begin{itemize}
			\item Uncertainty should reverse this, right?
			\item What is uncertainty? Make $v(z)$ stochastic is most natural
				\begin{itemize}
					\item I'm going to start with linear parameterization of $v(z)$ and add uncertainty. For now, take same form for $v(z)$
						\[
						  v(z) = \alpha -\beta \cdot z
						\]
						and take $z$ as a random variable distributed normally with mean $z$ and standard deviation $\sigma_z$. This is unfortunate nomenclature, since later we'll probably want to take this to a standard normal ``Z'' 
							\begin{itemize}
								\item This means that the legislators are ordered on the interval according to their ideal points, but there is acknowledged uncertainty surrounding their preferences 
								\item What is the source of this uncertainty? We take it to vary by legislator and also possibly by issue area when we extend the model to account for that
								\item Uncertainty comes from: log-rolling and cross-pressuring; length of voting record; electoral incentives that we can't control for
							\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

@@

\newpage
Notes from 3/16 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item Seems like FOC for lobby will boil down to each one buying votes until marginal benefit = marginal cost
	\item May want to use some simplified rule / heuristic for lobby's decision: perhaps they reorder the legislators by their $\pm 2$ std. dev. and make some decision based on that ordering who to lobby
	\item Will some kind of rule that looks like RMSE come out of the math? Is it possible to get anything closed-form at all?
\end{itemize}

\vskip.3in
Notes from 3/19 Skype chat (Kristy and Sebastian)
\begin{itemize}
	\item We can use the data we have to horse-race this model against other hypotheses about how lobbyists distribute bribes
		\begin{itemize}
			\item Allocate equally among legislators
			\item Groseclose Snyder with full information: only one side pays
			\item Our model with one dimension
				\begin{itemize}
					\item Could we use the econometric model to benchmark to one where uncertainty disappears? Or, as it does theoretically, does the model have to change completely?
				\end{itemize}
			\item Our model with multiple dimensions
		\end{itemize}
	\item We can think of this as looking for the effect of uncertainty on prices---we'd be pricing uncertainty relative to a model with uncertainty
		\begin{itemize}
			\item ``a metric in dollars of uncertainty''
			\item this is a model of vote buying under uncertainty
		\end{itemize}
	\item Given how different the environment with uncertainty is, Kristy should explore both the sequential model that parrots GS96 and a simultaneous model that is more like GH94 (menu auction)
	\item When mapping to the data, we're going to want to know from the model whether/when total contributions represent WTP.
		\begin{itemize}
			\item It clearly doesn't in the case of certainty. One side pays nothing; the other pays either as much as is necessary to shut down its opponent, or nothing at all the necessary amount exceeds WTP
			\item May be able to show it doesn't matter, that the proportion of total expenditures is a sufficient statistic
		\end{itemize}
	\item Finish writing the model, and then see if we can use the estimates we already have to write a first, very rough draft
\end{itemize}
